Verifying Demonstrations

### 2020-03-03 paper/DB-Schnorr-UWB.tex
Improves UWB section text

We will first present our version of the \ac{DB} Schnorr protocol for the 
mutual-trust case, where the prover and verifier have a pre-shared secret.
Then we will adapt it by introducing \iac{AKE}.
The authentication in this \ac{AKE} will leverage that our protocol is \iac{DB} 
\ac{ZKPK} for discrete logarithms.
If the \ac{AKE} is based on discrete logarithms we can prove the distance bound 
while we authenticate the key.
This allows us to embed this protocol into tamper resistant hardware to provide 
security against malicious provers.

@@

Thanks to \textcite{UWBPR} we can keep the Schnorr protocol 
almost as is, relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical 
layer.
The only concern, for now, is \acl{DBTF}.
(We deal with \acl{DBDF} later.)

@@

@@

The last property is \ac{DBTF}.
The protocol is \ac{DBTF} resistant.
Indeed, if the malicious prover gives more than one response to the accomplice, 
the accomplice can compute the secret key and, thus, impersonate forever.
And any help will increase the probability of success of future attempts.

\subsection{\Iacs*{DBDF} resistant protocol}

\Acl{DB} protocols requires hardware implementations.
We will use a trusted hardware implementation to overcome the limitation of 
\textcite{UWBPR}, \ie that the prover and verifier be mutually trusted.
We will need \iac{PKI} for the verifier to verify the trusted hardware.
We will leverage this \ac{PKI} to overcome the shared-key requirement.
With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
\ac{ZKPK} which \emph{simultaneously} proves
\begin{enumerate*}
\item that the protocol is run by trusted hardware,
\item that that trusted hardware is within proximity,
\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
\item that that knowledge is within proximity.
\end{enumerate*}

>>>>

We will first present our version of the \ac{DB} Schnorr protocol for the 
mutual-trust case, where the prover and verifier have a pre-shared secret.
Then we will adapt it by introducing \iac{AKE} protocol.
The authentication in this \ac{AKE} will leverage that our protocol is \iac{DB} 
\ac{ZKPK} for discrete logarithms.
If the \ac{AKE} is based on discrete logarithms we can prove the distance bound 
while we authenticate the key.
This allows us to embed this protocol into tamper resistant hardware to remove 
the mutual-trust requirement.

@@

Thanks to \textcite{UWBPR} we can keep the Schnorr protocol almost as is, since 
relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical layer.
\Ac{DBDF} is not a concern either, since the prover is trusted.
The only concern, for now, is \acl{DBTF}.
(However, we will still prove those properties, as they will be useful later.)

@@

The protocol is \ac{DBTF} resistant.
Indeed, if the malicious prover gives more than one response to the accomplice, 
the accomplice can compute the secret key and, thus, impersonate forever.
And any help will increase the probability of success of future attempts.

@@

\subsection{From mutual trust to \acs*{PKI}}

\Acl{DB} protocols requires hardware implementations.
We will use a \emph{trusted} hardware implementation to overcome the limitation 
of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
We will need \iac{PKI} for the verifier to verify the trusted hardware.
We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
any two devices in this \ac{PKI} to perform \acl{DB}.
With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
\ac{ZKPK} which \emph{simultaneously} proves
\begin{enumerate*}
\item that the protocol is run by trusted hardware,
\item that that trusted hardware is within proximity,
\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
\item that that knowledge is within proximity.
\end{enumerate*}
